Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Distributed Deep Convolutional Compression for Massive MIMO CSI Feedback

@@

>>>>

\cite{mashhadi2020deepcmc}Proposes DeepCMC, a fully convolutional autoencoder with quantization and entropy coding blocks that achieves 3--5~dB lower NMSE than \cite{abe} at equivalent bit rates. Extends to a distributed version exploiting inter-user CSI correlations, reducing feedback overhead by 17--50\% for nearby users (<1m spacing) compared to single-user compression.

@@

	\bibitem{mashhadi2020deepcmc}
	M.~B.~Mashhadi, Q.~Yang, and D.~Gunduz, ``Distributed deep convolutional compression for massive MIMO CSI feedback,'' \textit{IEEE Trans. Wireless Commun.}, vol.~19, no.~8, pp.~5317--5328, Aug.~2020.
